\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}

% Custom Colors
\definecolor{primary}{HTML}{2C3E50}
\definecolor{secondary}{HTML}{E74C3C}
\definecolor{accent}{HTML}{3498DB}

% Style Config
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{primary}{Strategic ROI Report}}
\lhead{\textcolor{primary}{Dedicated Agent Control}}
\rfoot{Page \thepage}

\title{\LARGE \textbf{\textcolor{primary}{High-Octane Agent Control Systems}} \\ \large \textit{Optimal OS Configuration for Dedicated Agent Autonomy}}
\author{Jarvis (Prompt Architect)}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{fancy}

\section{Executive Summary}
To maximize ROI and remove operational friction, a separate computer for agentic control (Agent Zero, OpenClaw, and general autonomous frameworks) is highly recommended. This report identifies the optimal hardware-software stack to ensure 24/7 persistence, security, and performance.

\section{Agent-Specific Requirements}

\subsection{Agent Zero}
\begin{itemize}
    \item \textbf{Environment:} Docker is mandatory for safety.
    \item \textbf{Performance:} Python-based; thrives in environments with low I/O latency.
    \item \textbf{OS Preference:} Native Linux (Ubuntu) for direct socket access and Docker performance parity.
\end{itemize}

\subsection{OpenClaw (Optimized Setup)}
As researched from the latest power-user documentation (Moritz Kremb interview):
\begin{itemize}
    \item \textbf{Persistence:} Requires a 30-minute heartbeat for auto-saving state.
    \item \textbf{Interface:} Telegram-native UI allows for remote mobile operation.
    \item \textbf{Cost Optimization:} OAuth integration with ChatGPT/Anthropic subscriptions significantly reduces per-token API overhead.
\end{itemize}

\subsection{GaG (General Agent Gateways)}
Refers to autonomous local frameworks (e.g., GAIA, Godmode-like setups). These require:
\begin{itemize}
    \item \textbf{Headless Operation:} Stable background processes without GUI overhead.
    \item \textbf{Local Inference:} Support for Ollama or vLLM to keep data private and lower latency.
\end{itemize}

\section{OS Comparison Analysis}

\begin{itemize}
    \item \textbf{Ubuntu 24.04 LTS (Recommended):} The industry standard for reliability. Zero bloat (Server version) or standard Desktop for ease of troubleshooting. Native Docker support is flawless.
    \item \textbf{Proxmox VE:} The "Power User" choice. Allows running Agent Zero and OpenClaw in isolated virtual environments. Snapshot capabilities allow for "Undo" on system-breaking agent actions.
    \item \textbf{Windows 11 + WSL2:} High overhead, but best for compatibility with Windows-only software if needed.
\end{itemize}

\section{Final Recommendation: The "Best Course of Action"}
\textbf{Hardware:} A dedicated Mini-PC (Intel NUC or Mac Mini M2/M4) with $\geq$32GB RAM and an NVMe SSD. \\
\textbf{OS:} \textcolor{secondary}{\textbf{Ubuntu 24.04 Server}} with a lightweight GUI (optional). \\
\textbf{Remote Access:} \textbf{Tailscale} for secure, zero-config access from your main Windows workstation.

\section{Immediate Next Steps}
\begin{enumerate}
    \item Secure dedicated hardware.
    \item Flash Ubuntu 24.04 LTS.
    \item Install Docker, Portainer, and Tailscale.
    \item Clone OpenClaw/Agent Zero repositories and initiate the "Morning Report" automation.
\end{enumerate}

\end{document}
