\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{xcolor}

% Custom Colors
\definecolor{primary}{HTML}{2C3E50}
\definecolor{secondary}{HTML}{E74C3C}

\title{\LARGE \textbf{\textcolor{primary}{Strategic Agent OS Report}} \\ \large \textit{Optimal Configuration for Dedicated Agent Control}}
\author{Jarvis (Prompt Architect)}
\date{\today}

\begin{document}

\maketitle

\section{Executive Summary}
To maximize ROI and remove operational friction, a separate computer for agentic control (Agent Zero, OpenClaw, and general autonomous frameworks) is highly recommended. This report identifies the optimal hardware-software stack to ensure 24/7 persistence, security, and performance.

\section{Agent-Specific Requirements}

\subsection{Agent Zero}
\begin{itemize}
    \item \textbf{Setup:} Primarily Docker-based for safety and isolation.
    \item \textbf{OS Preference:} Native Linux (Ubuntu) is the gold standard for performance.
\end{itemize}

\subsection{OpenClaw (Optimized Setup)}
As researched from the Moritz Kremb power-user interview:
\begin{itemize}
    \item \textbf{Persistence:} Deploy with a 30-minute heartbeat for state retention.
    \item \textbf{Interface:} Telegram-native UI is superior for multi-device control.
    \item \textbf{Savings:} OAuth via existing ChatGPT/Anthropic subscriptions drastically reduces costs.
\end{itemize}

\subsection{GaG / Autonomous Frameworks}
Refers to high-autonomy frameworks (GAIA-like):
\begin{itemize}
    \item \textbf{Core need:} Stable background processes and local LLM support via Ollama.
\end{itemize}

\section{OS Comparison Analysis}

\begin{itemize}
    \item \textbf{Ubuntu 24.04 LTS (Winner):} Flawless Docker support and lowest resource overhead.
    \item \textbf{Proxmox VE (Alpha Choice):} Superior for power users who need snapshots and multi-agent isolation.
    \item \textbf{Windows 11 + WSL2:} Viable if familiar GUI is required, but less efficient for 24/7 headless duty.
\end{itemize}

\section{Course of Action}
\textbf{Hardware:} Dedicated Mini-PC (i7/32GB RAM). \\
\textbf{OS:} \textcolor{secondary}{\textbf{Ubuntu 24.04 LTS}}. \\
\textbf{Remote Access:} \textbf{Tailscale} for secure connection from your main Windows machine.

\end{document}
