\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Audit Report: OpenClaw Masterclass}
\author{Jarvis (Agentic Audit)}
\date{March 23, 2026}

\begin{document}
\maketitle

\section{Overview}
Analysis of the video: \textit{"I fixed OpenClaw so it actually works (full setup)"} by Greg Isenberg & Moritz Kremb. This report details the 10-step optimization framework for autonomous personal agents.

\section{The 10-Step Optimization Framework}
\begin{enumerate}
    \item \textbf{Troubleshooting Baseline:} Create an "OpenClaw Support" project in Claude/ChatGPT using up-to-date documentation via \texttt{Context 7}.
    \item \textbf{Personalization:} Optimize workspace files (\texttt{agents.md}, \texttt{soul.md}, \texttt{user.md}, \texttt{identity.md}).
    \item \textbf{Memory Persistence:} Use \texttt{memory.md} for long-term insights and Heartbeat for auto-saving session data.
    \item \textbf{Model Selection (OAuth):} Leverage existing \$20/month subscriptions for ChatGPT/Anthropic to keep costs low.
    \item \textbf{Telegram Organization:} Use specific Groups and Topics with area-focused system prompts.
    \item \textbf{Browser Modes:} Master the use of WebFetch, Managed Local Browser, and Chrome Relay.
    \item \textbf{Skills Repository:} Enable built-in skills (1Password, Apple Notes) and audit marketplace skills (Clawhub).
    \item \textbf{Heartbeat.md:} Configure a 30-minute maintenance cycle for to-dos and cron health.
    \item \textbf{Security:} Prefer local MacOS over VPS; mitigate prompt injection with high-tier models.
    \item \textbf{Least Access:} Use dedicated agent-owned Google/X accounts and granular Notion access.
\end{enumerate}

\section{Key Real-World Use Cases}
\subsection{No AI Slop Content Engine}
A 7-step automated pipeline for continuous idea capture (YouTube/X/Telegram), script generation based on style libraries, and automated cross-platform posting.

\subsection{Conversational CRM}
A Sheets-based lead management system integrated with Gmail, Calendar, and WhatsApp for automated follow-ups and meeting coordination.

\section{Conclusion}
OpenClaw represents the "new computer" era. Resilient setup requires local execution, high-tier models for security, and persistent memory maintenance.

\end{document}
